\chapter{Summary and Outlook}
\label{summary}
 
\section{Summary}

By way of this project paper we have assessed and described the state of the art for current technologies in the areas of 
containerized software, container orchestration and how those tie in with Software defined infrastructure.
We have done the same for the state of the art in the solution of complex problems found in the field of and  solved with \ac{HPC},
namely the two larger classes of problems, \ac{LCP} and \ac{TCP} problems, and what strategies are usually employed to solve those problems.

We have then addressed the problems identified by the problem statement with the statement of an initial goal, 
and structured an intervention to solve those problems by way of the creation of a prototype.
Before the iterative process of prototyping could begin we had to make a non-trivial decision on the choice of a container orchestrator/ workflow manager.
For which we defined, discussed and weighted the selection criteria, and then evaluated the available options against those criteria, and 
We found our best fit through the employment of the \ac{SMART-ER} method, which was the \ac{k8s}-based orchestrator named Pachyderm.

The iterative process of prototyping was split into three main areas of focus, the infrastructure, the solution to \acp{TCP} and the integration of a complete 
\ac{CI/CD} pipeline. Each of these areas was given at least two iterations and the results of each iteration were documented, evaluated and recommendations for
future iterations were made.

The final results of the prototype were then evaluated against the initial goal and the problems identified in the problem statement,
and the resulting artifact was found to be a valid form of intervention to solve the problems identified in the problem statement,
while still being limited in scope and applicability, as was to be expected from a non production prototype. 


\section{Outlook}

As already discussed, the limiting factor of this project was the available time, which left many avenues to still be explored
both in respect to the prototype itself, and how it can be further extended to explore avenues not yet addressed by this project.

Of most importance in this case would be a further exploration of an efficient solution to \ac{TCP} problems, 
as the current solution does technically work, but is lacking the efficiencies to be a viable solution for large scale problems.
An initial starting point for this could be the network stack in between the containers and the underlying network infrastructure.
